Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-12 trunk/draft/Results.tex
now it 9 - appril and after club day
12-4

\chapter{Evaluation}

This chapter discribes and illustrates the experiments performed on the system. In the chapter, section \ref{sec:ExperimentsSetup} describes the experimental setup. Section \ref{sec:Datasets} describes the datasets used. Section \ref{sec:ResultsDetails} demonstrates and analyzes the results.

The system has two main parts the DPSO stroke segmenation and symbol recogntion. Each part is evaluated sperately. The preprocessing procedures and computation is evaluated using their effect on the segmentation algorithm. These results are reported in section \ref{sec:ResultsDetails}. The effect of number of agents, the error thresholds and various other PSO paramters are investigated in Section \ref{sec:PSO}. The results presented in Section \ref{sec:ResultsDetails} and \ref{sec:PSO}.

@@

%The accuracy is computed as the number of correctly recognized samples divided by the total number of samples in the test.

%The recognition system evalutation is presented in Section \ref{sec:SegmentationAlgorithms}. The

%The variable used to tune the swarm algorithm were tested to choose the best parameters to use
\section{Datasets}
\label{sec:Datasets}
Two different data set were used, 
%For classifier and algorithm testing the system used a data set collected by
\begin{description}
	\item [Heloise Dataset] Data set collected by \cite{HeloiseBeautification} and was previously used by \cite{Oltmans07} as benchmarck for sketch recognition problem. The data are drawn by 16 users each of them have drawn from 30 to 50 samples for each shape. Figure \ref{fig:symbolSet} shows the shapes used in the data set. The dataset was divided into training set and test set. Four different splits for the training and test data are generated from the dataset. %The results displayed are the average recognition accuracy of the four splits resulted from the classifier after recognizing the symbols.
		\item [MultiDomain Dataset] A dataset we collected manually from different users. The dataset contains symbols from three diffrent domains ( UML, mechanical and electrical engineering symbols). Data are collected from 4 different users each of them have drawn from 20 to 40 samples of each shapes. Figure \ref{fig:MultisymbolSet} shows some of the shapes used in the dataset. The dataset was divided into training set and test set. Four different splits for the training and test data are generated from the dataset. %The results displayed are the average recognition accuracy of the four splits resulted from the classifier after recognizing the symbols. 
\end{description}
 %We divided the dataset equally into training set and test set.  The results displayed are the recognition accuracy resulted from the classifier after recognizing the symbols. \\
%We divided the dataset into four sets each set contains four different users. Furthermore, each set is divided into train and test set where the trained set where used to train the classifiers and the test set where used for testing.  The algorithms are then tested using the four sets and the results are averaged.
\begin{figure}[]\centering
\fbox{  \parbox{8cm}{% 
		\includegraphics[scale=0.7]{images/symbolSet.eps}	}
		}
	\caption{The Symbol Set}
	\label{fig:symbolSet}
\end{figure}

\begin{figure}[]\centering
\fbox{  \parbox{8cm}{% 
		\includegraphics[scale=0.7]{images/symbolSet.eps}	}
		}
	\caption{The MultiDomain Dataset }
	\label{fig:MultisymbolSet}
\end{figure}

@@

\begin{description}
	\item[Segmentation Error] The segmentation error is computed from each stroke after segmentation as computed from Equation \ref{} in Section \ref{}. 
	\item [Recognition accuracy] We measure recognition performance for each algorithm by determining the number of correctly identified symbols in the whole dataset. Note that All the results are shown as the average of the four split of the dataset used. 
\end{description}

>>>>

\chapter{Evaluation}
\label{sec:Evaluation}
This chapter discribes and illustrates the experiments performed on the system. In the chapter, section \ref{sec:ExperimentsSetup} describes the experimental setup. Section \ref{sec:Datasets} describes the datasets used. Section \ref{sec:ResultsDetails} demonstrates and analyzes the results.

The system has two main parts the DPSO stroke segmenation and symbol recogntion. Each part is evaluated sperately. The preprocessing procedures and computation is evaluated using their effect on the segmentation algorithm. These results are reported in section \ref{sec:ResultsDetails}. The effect of number of agents, the error thresholds and various other PSO paramters are investigated in Section \ref{sec:PSO}. %The results presented in Section \ref{sec:ResultsDetails} and \ref{sec:PSO}.

@@

%The accuracy is computed as the number of correctly recognized samples divided by the total number of samples in the test. 
%The recognition system evalutation is presented in Section \ref{sec:SegmentationAlgorithms}. The  
%The variable used to tune the swarm algorithm were tested to choose the best parameters to use

\section{Datasets}
\label{sec:Datasets}
Two different data set were used, 
%For classifier and algorithm testing the system used a data set collected by
\begin{description}
	\item [Heloise Dataset] Data set collected by \cite{HeloiseBeautification} and was previously used by \cite{Oltmans07} as benchmarck for sketch recognition problem. The data are drawn by 16 users each of them have drawn from 30 to 50 samples for each shape. Figure \ref{fig:symbolSet} shows the shapes used in the data set. The dataset was divided into training set and test set. Four different splits for the training and test data are generated from the dataset. In worth noting that \cite{HeloiseBeautification} and \cite{Oltmans07} achieved 96.7\% and  94.4\%  on the dataset respecitvily. %, 94.4\%  , which
is comparable to the 96.7%  %The results displayed are the average recognition accuracy of the four splits resulted from the classifier after recognizing the symbols.
		\item [MultiDomain Dataset] A dataset we collected manually from different users. The dataset contains symbols from three diffrent domains ( UML, mechanical and electrical engineering symbols). Data are collected from 4 different users each of them have drawn from 20 to 40 samples of each shapes. Figures \ref{fig:LogicSet} and \ref{fig:ElectSet} show some of the shapes used in the dataset. Symbols from different domains were gathered to evaluate the system thourhgtout different types of shapes. Useres were requested to draw symbols without any restriction on style,size or orientations. The dataset was divided into training set and test set. Four different splits for the training and test data are generated from the dataset. %The results displayed are the average recognition accuracy of the four splits resulted from the classifier after recognizing the symbols. 
\end{description}
 %We divided the dataset equally into training set and test set.  The results displayed are the recognition accuracy resulted from the classifier after recognizing the symbols. \\
%We divided the dataset into four sets each set contains four different users. Furthermore, each set is divided into train and test set where the trained set where used to train the classifiers and the test set where used for testing.  The algorithms are then tested using the four sets and the results are averaged.
\begin{figure}[]\centering
\fbox{  \parbox{8cm}{% 
		\includegraphics[scale=0.7]{images/symbolSet.eps}	}
		}
	\caption{The Symbol Set}
	\label{fig:symbolSet}
\end{figure}

\begin{figure}[]\centering
\fbox{  \parbox{6cm}{% 
		\includegraphics[scale=0.7]{images/logicSymbols.eps}	}
		}
	\caption{Example of Logic Symbols}
	\label{fig:LogicSet}
\end{figure}
\begin{figure}[]\centering
\fbox{  \parbox{8cm}{% 
		\includegraphics[scale=0.7]{images/SymbolsElectricalr.eps}	}
		}
	\caption{Example of Electrical Symbols}
	\label{fig:ElectSet}
\end{figure}

@@

\begin{description}
	\item[Segmentation Error] The segmentation error is computed from each stroke after segmentation as computed from Equation \ref{eq:bestFit1} and \ref{eq:bestFit2}. 
	\item [Recognition accuracy] We measure recognition performance for each algorithm by determining the number of correctly identified symbols in the whole dataset. Note that All the results are shown as the average of the four split of the dataset used. 
\end{description}
